\bf Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-08-26 paper.qmd
Need to complete section 6

In this section, the effectiveness of the algorithm is described using a simulated dataset. The dataset consists of five spherical Gaussian clusters in $4\text{-}D$, with each cluster containing an equal number of points and the same within-cluster variation.

>>>>

In this section, we will assess how t-SNE, UMAP, and PaCMAP algorithms preserve the clustering structure. We will use a simulated dataset consisting of five spherical Gaussian clusters where each cluster occupies a different corner of the $4\text{-}D$ space, with each cluster containing an equal number of points ($1000$) and the same within-cluster variation. The data simulated from $\Sigma = \begin{pmatrix}
0.0025 & 0 & 0 & 0 \\
0 & 0.0025 & 0 & 0 \\
0 & 0 & 0.0025 & 0 \\
0 & 0 & 0 & 0.0025 \\
\end{pmatrix}$.

<!-- In this section, the effectiveness of the algorithm is described using a simulated dataset. The dataset consists of five spherical Gaussian clusters in $4\text{-}D$, with each cluster containing an equal number of points and the same within-cluster variation. -->

### 2024-08-26 paper.tex
Need to complete section 6

In this section, the effectiveness of the algorithm is described using a
simulated dataset. The dataset consists of five spherical Gaussian
clusters in \(4\text{-}D\), with each cluster containing an equal number
of points and the same within-cluster variation.

>>>>

In this section, we will assess how t-SNE, UMAP, and PaCMAP algorithms
preserve the clustering structure. We will use a simulated dataset
consisting of five spherical Gaussian clusters where each cluster
occupies a different corner of the \(4\text{-}D\) space, with each
cluster containing an equal number of points (\(1000\)) and the same
within-cluster variation. The data simulated from
\(\Sigma = \begin{pmatrix}
0.0025 & 0 & 0 & 0 \\
0 & 0.0025 & 0 & 0 \\
0 & 0 & 0.0025 & 0 \\
0 & 0 & 0 & 0.0025 \\
\end{pmatrix}\).
